---
title: "HW(1)"
author: "Mikaela Olaya" # your name
date: "2/5/2022" # today
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, eval = TRUE)
```

#Run this code first
```{r, include=FALSE}
if (!require('ggplot2')) install.packages('ggplot2'); library('ggplot2') 
```

***
### If you don't know the answer, leave it blank. If you are caught cheating, you will be given minus 50 points.   
***

Q1. Replace the author name with your name in YAML part above. 

Q2. Store five values `82.0, 31.2, 98.2, 19.4, 72.6` into the `scores` variable.
```{r}
scores <- c(82.0, 31.2, 98.2, 19.4, 72.6)
```

Q3. Write a code that finds the minimun value of `scores` that you have created in Q2.
```{r}
min(scores)
```

Q4. Assign the value of 4 raised to 2 to a variable `generation`. Then, print out the value of `generation`.
```{r}
generation <- 4^2
print(generation)
```

Q5. Assign the value of square root 81 to a variable `nine`, and print out `nine`.
```{r}
nine <- sqrt(81)
print(nine)
```

Q6. Store a text `mozart` into the variable `piano`.
```{r}
piano <- "mozart"
```

Q7. What are three components for a single plot of `ggplot2` package? 
```{r}

#Data, Mapping, and Geom 

```

Q8. A line of code that shows `presidential` data as a table
```{r}
View(presidential)
```

Q9. Create a matrix with 4 rows that contain the numbers 1 up to 12
```{r}
matrix(1:12, byrow= FALSE, nrow=4)
```

Q10. A line of code that assigns `displ` column as `x-axis` and `hwy` column as `y-axis` of `mpg` data to a variable `mpg_plot` using `ggplot2` package
```{r}
mpg_plot <- ggplot(data=mpg, aes(x= displ, y= hwy))
```

Q11. Two lines of code that create a scatter plot of a variable `mpg_plot` that you have made in Q10 
```{r}
mpg_plot+
  geom_point()
```

Q12. Three lines of code that create subplots (four rows) by `class` column, using two lines of code for Q10.
```{r}
mpg_plot +
  geom_point()+
  facet_wrap(~class, nrow=4)
```

Q13. A line of code that returns dimension information of `presidential` data
```{r}
dim(presidential)
```

Q14. What are the unique values of `party` column of `presidential` data?
```{r}
unique(presidential$party)
```

Q15. Two lines of code that will directly create a simple stacked bar plot that shows the count by `class` column of `mpg` data with filling color by `trans` column

```{r}
ggplot(data=mpg, aes(x=class, fill= trans))+
  geom_bar()
```

Q16. A line of code that assigns `state` column as `x` position of `midwest` data to a variable `midwest_plot` using `ggplot2` package
```{r} 
midwest_plot <- ggplot(data=midwest,aes(x= state))
```

Q17. Five lines of code that will return a bar plot of the `midwest_plot` variable with a title `Plot of count by state`. X-axis is labeled as `state` and y-axis as `count`. 
```{r}
midwest_plot +
  geom_bar()+
  ggtitle("Plot of count by state")+
  xlab("state")+
  ylab("count")
```

Q18. What is the name of 7th column of `diamonds` dataset?
```{r}
colnames(diamonds[,7])
```

Q19. How many columns and rows does `midwest` data have?
```{r}
dim(midwest)
```

Q20. Two different commands for a quick overview of `mpg` data that we have learned in our class
```{r}
summary(mpg)
str(mpg)
```

### *End of document*
