---
title: "Onboarding Test"
author: "Mikaela Olaya"
date: "1/9/2022"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## Welcome to INFO 3221

This document is designed to test if your set-up is successful. Please follow the instructions below. Replace the name of author with yours and date with today above. Do not change other information.    

#Step1. Table

- Place the cursor at the end of the code (right after 'summary(cars)') and hit ctrl+enter (Windows), command+enter(Mac). You will get a table. 

```{r cars}
summary(cars)
```

#Step2. Plot

- Place the cursor at the end of the code (right after 'plot(pressure)') and hit ctrl+enter (Windows), command+enter(Mac). You will have a figure. 

```{r pressure, echo=TRUE}
plot(pressure)
```

#Step3. Save this file as onboarding.Rmd

- Tip: You will have a bunch of codes every class, so it would be better for you to create a folder named 'INFO3221' and then create subfolders like 'Class-1' for all the classes during the semester.

#Step4. Click the 'Knit' icon above, and then you will automatically 1) have a PDF pop-up window and 2) be able to find 'onboarding.pdf' in the same folder where you saved 'onboarding.Rmd' file. 

- If 'Knit' icon does not work, please let me know. 

#Step5. Upload both 1) onboarding.Rmd and 2) onboarding.pdf files to Canvas > Modules > Class-1 > System set-up > Onboarding test assignment.

#That's it. Thank you. 
